---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# daplot

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of daplot is to provide a simplified interface for creating a plot with a dual axis in ggplot2.

## Installation

You can install the development version of daplot from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("TeroJii/daplot")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(daplot)
## basic example code
```


```{r cars}
cars |> 
  daplot::daplot()
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = TRUE}
# empty placeholder
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
