---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# daplot

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/TeroJii/daplot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/TeroJii/daplot/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of daplot is to provide a simplified interface for creating a plot with a dual axis in ggplot2.

## Installation

You can install the development version of daplot from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("TeroJii/daplot")
```

## Motivation

The package [ggplot2](https://ggplot2.tidyverse.org/) provides an incredibly rich and extensive functionality for creating a variety of plots.
Let's take the following visualization as an example:

```{r ggplot-example}
library(ggplot2)

mtcars |> 
  ggplot(aes(x = mpg)) +
  geom_line(aes(y = wt), color = "blue") +
  geom_line(aes(y = qsec), color = "red")
```



```{r example}
library(daplot)

mtcars |> 
  daplot(mpg, wt, qsec, y1_label = "test label")
```



